Concave reduction in Self-healing swarms

### 2018-10-18 paper.tex
Updates

\title{Towards a self-healing swarm through the removal of voids and anomalies}

@@

{Eliot \headeretal: Towards a self-healing swarm through the removal of voids and anomalies}
{Eliot \headeretal: Towards a self-healing swarm through the removal of voids and anomalies}

@@

%COVERBASELINESTART.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/ConcaveInitial}{Initial Swarm Deployment\label{fig:ConcaveInitial}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcaveEffectDist}{Baseline/Concave effect using distance metric\label{concave:BaselineConcaveEffectDist}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectDist}
%% \end{center}
%% \caption{Baseline/Concave effect distance \label{concave:BaselineConcaveEffectDist}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcaveEffectMag}{Baseline/Concave effect using cohesion/repulsion\label{concave:BaselineConcaveEffectMag}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectMag}
%% \end{center}
%% \caption{Baseline/Concave effect magnitude\label{concave:BaselineConcaveEffectMag}}
%% \end{figure}

Figure~\ref{concave:BaselineConcavePerimeter} shows the effect on the number of perimeter agents. Initially the perimeter size is minimally affected due to the swarms compression however after the expansion phase of the swarm (8 seconds) more perimeter agents are identified as concave edges are formed. As these concave edges are `straightened' they create further anomalies that ripple through the swarm. This rippling is identified by the erratic changes in the number of perimeter agents. After approximately 30 seconds the swarm has been forced into a less angular structure with curved edges and the number of perimeter agents falls below the minimum of the baseline. The shape of the swarm is still undergoing change following this and the perimeter count continues to fluctuate.
%PERIMETER8070CONCAVE.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcavePerimeter}{Baseline/Concave perimeter size\label{concave:BaselineConcavePerimeter}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcavePerimeter}
%% \end{center}
%% \caption{Baseline/Concave perimeter size\label{concave:BaselineConcavePerimeter}}
%% \end{figure}
The effect on the structure of the swarm caused by the concave perimeter agents moving towards the gap agents is to pull the internal agents forward. This pulling causes the swarm to develop a more rounded structure but the effect also have a negative impact. If the tolerance of the agent's movements (the difference between the agent ranges for repulsion and cohesion) is too small then the distortion effect of the concave reduction can create additional voids. The perimeter agents will then move so as to remove the defect~(Fig.~\ref{fig:OuterPerimeterJitter1}). Following the void creation the agents are now impacted by a second concave reduction from the newly created void and the anomaly on the perimeter edge `snaps' back closing the void~(Fig.~\ref{fig:OuterPerimeterJitter2}). This process repeats itself creating an instability in the number of perimeter agents which is highlighted in~Fig.~\ref{concave:BaselineConcavePerimeter} as the erratic change in the number of agents.

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcaveEffectPath1}{Baseline/Concave path effect (Full)\label{concave:BaselineConcaveEffectPath1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectPath1}
%% \end{center}
%% \caption{Baseline/Concave path effect\label{concave:BaselineConcaveEffectPath1}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcaveEffectPath2}{Baseline/Concave path effect (Zoomed)\label{concave:BaselineConcaveEffectPath2}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectPath2}
%% \end{center}
%% \caption{Baseline/Concave path effect\label{concave:BaselineConcaveEffectPath2}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcaveEffectDist8060}{Baseline/Concave effect distance (80/60)\label{concave:BaselineConcaveEffectDist8060}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectDist8060}
%% \end{center}
%% \caption{Baseline/Concave effect distance (80/60)\label{concave:BaselineConcaveEffectDist8060}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcaveEffectMag8060}{Baseline/Concave effect magnitude (80/60)\label{concave:BaselineConcaveEffectMag8060}}
% \begin{figure}
% \begin{center}
% \includegraphics[width=8cm]{figures/BaselineConcaveEffectMag8060}
% \end{center}
% \caption{Baseline/Concave effect magnitude (80/60)\label{concave:BaselineConcaveEffectMag8060}}
% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcavePerimeter8060}{Baseline/Concave perimeter size (80/60)\label{concave:BaselineConcavePerimeter8060}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcavePerimeter8060}
%% \end{center}
%% \caption{Baseline/Concave perimeter size (80/60)\label{concave:BaselineConcavePerimeter8060}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/Baseline8060End}{Baseline end\label{fig:BaselineEndPoint}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/Baseline8060End}
%% \end{center}
%% \caption{Baseline end\label{fig:BaselineEndPoint}}
%% \end{figure}
%COVERBASELINE8060COMPRESSEND.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/Concave8060End}{Concave reduction end\label{fig:ConcaveEndPoint}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/Concave8060End}
%% \end{center}
%% \caption{Concave reduction end\label{fig:ConcaveEndPoint}}
%% \end{figure}

@@

%COVERBASELINE8060.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcaveEffectPath80601}{Baseline/Concave path effect (80/60)\label{concave:BaselineConcaveEffectPath80601}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectPath80601}
%% \end{center}
%% \caption{Baseline/Concave path effect (80/60)\label{concave:BaselineConcaveEffectPath80601}}
%% \end{figure}

%COVERBASELINE8060.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/BaselineConcaveEffectPath80602}{Baseline/Concave path effect (80/60)\label{concave:BaselineConcaveEffectPath80602}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectPath80602}
%% \end{center}
%% \caption{Baseline/Concave path effect (80/60)\label{concave:BaselineConcaveEffectPath80602}}
%% \end{figure}
With the tolerance levels set appropriately the impact of the concave reduction is to reduce the number of agents being identified as coordinators~(Fig.~\ref{concave:mobileSwarm1}). This reduction in perimeter size is due to a reduction in the number of anomalies in the swarm. The effect of the concave reduction on a convex (outer) perimeter is limited when a swarm is deployed in an almost circular manner as there is limited space for optimisation. The effect is more pronounced when a swarm is `malformed' with large anomalies producing concave edges.

@@

%COVERBASELINE4560-BASEEND.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/Baseline4560End}{Baseline end\label{fig:BaselineEndPoint4560}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Baseline4560End}
%% \end{center}
%% \caption{Baseline end\label{fig:BaselineEndPoint4560}}
%% \end{figure}

%COVERBASELINE4560END3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/Concave4560End}{Concave end\label{fig:ConcaveEndPoint4560}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Concave4560End}
%% \end{center}
%% \caption{Concave end\label{fig:ConcaveEndPoint4560}}
%% \end{figure}

@@

%COVERBASELINE4560.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/Concave4560-1}{Initial\label{fig:VoidConcaveReduction1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Concave4560-1}
%% \end{center}
%% \caption{Initial\label{fig:VoidConcaveReduction1}}
%% \end{figure}

%COVERBASELINE4560END2.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/Concave4560-2}{Partial\label{fig:VoidConcaveReduction2}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Concave4560-2}
%% \end{center}
%% \caption{Partial\label{fig:VoidConcaveReduction2}}
%% \end{figure}

%COVERBASELINE4560END3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/Concave4560-3}{Complete\label{fig:VoidConcaveReduction3}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Concave4560-3}
%% \end{center}
%% \caption{Complete\label{fig:VoidConcaveReduction3}}
%% \end{figure}

@@

%SWARMHOLE-DIST-4560.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/ConcavePerimeter4560-DIST}{Concave reduction stability effect distance\label{voids:ConcavePerimeter4560-DIST}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/ConcavePerimeter4560-DIST}
%% \end{center}
%% \caption{Concave reduction stability effect distance\label{voids:ConcavePerimeter4560-DIST}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/ConcavePerimeter4560-DIST-2}{Concave reduction stability effect distance\label{voids:ConcavePerimeter4560-DIST-2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/ConcavePerimeter4560-MAG}{Concave reduction stability effect magnitude\label{voids:ConcavePerimeter4560-MAG}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/ConcavePerimeter4560-MAG-2}{Concave reduction stability effect magnitude\label{voids:ConcavePerimeter4560-MAG-2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/ConcavePerimeter4560-1}{Concave reduction perimeter effect\label{methods:ConcavePerimeter4560-1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/SwarmCoverage4560-1}{Agent movement comparison\label{voids:SwarmCoverage4560-1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/SwarmCoverage4560-2}{Agent movement comparison\label{voids:SwarmCoverage4560-2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=10cm]{figures/OilSlick}{Concave reduction oil slick surrounding\label{voids:OilSlick}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/OilSlick}
%% \end{center}
%% \caption{Concave reduction oil slick surrounding\label{voids:OilSlick}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=10cm]{figures/OilSpillSimulator}
{Oil spill containment simulation\label{concave:OilSpillSimulation}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/OilSpillSimulator}
%% \end{center}
%% \caption{Oil spill containment simulation\label{concave:OilSpillSimulation}}
%% \end{figure}

@@

%COVERBASELINE8060OILSPILL1.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillBase1}{Initial\label{concave:OilSpillBase1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[with=5cm]{figures/OilSpillBase1}
%% \end{center}
%% \caption{Initial\label{concave:OilSpillBase1}}
%% \end{figure}
%COVERBASELINE8060OILSPILL3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillBase2}{Partial\label{concave:OilSpillBase2}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillBase2}
%% \end{center}
%% \caption{Partial\label{concave:OilSpillBase2}}
%% \end{figure}
%COVERBASELINE8060OILSPILL3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillBase3}{End\label{concave:OilSpillBase3}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillBase3}
%% \end{center}
%% \caption{End\label{concave:OilSpillBase3}}
%% \end{figure}

@@

%COVERBASELINE8060OILSPILLCONCAVE1.py 
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillConcave1}{Initial\label{concave:OilSpillConcave1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillConcave1}
%% \end{center}
%% \caption{Initial\label{concave:OilSpillConcave1}}
%% \end{figure}

%COVERBASELINE8060OILSPILLCONCAVE2.py 
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillConcave2}{Partial\label{concave:OilSpillConcave2}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillConcave2}
%% \end{center}
%% \caption{Partial\label{concave:OilSpillConcave2}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillConcave3}{End\label{concave:OilSpillConcave3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillPerimeter8060-DIST-1}{Oil spill containment distance\label{concave:OilSpillPerimeter8060-DIST-1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillPerimeter8060-MAG-1}{Oil spill containment magnitude\label{concave:OilSpillPerimeter8060-MAG-1}}

@@

%PERIMETEROILSPILL.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=18cm]{figures/OilSpillPerimeter8060-1}{Swarm perimeter size comparison\label{concave:OilSpillPerimeter8060-1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/OilSpillPerimeter8060-1}
%% \end{center}
%% \caption{Swarm perimeter size comparison\label{concave:OilSpillPerimeter8060-1}}
%% \end{figure}

>>>>

\title{Concave reduction in Self-healing swarms}

@@

{Eliot \headeretal: Concave reduction in Self-healing swarms}
{Eliot \headeretal: Concave reduction in Self-healing swarms}

@@

%COVERBASELINESTART.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/ConcaveInitial}{Initial Swarm Deployment\label{fig:ConcaveInitial}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcaveEffectDist}{Baseline/Concave effect using distance metric\label{concave:BaselineConcaveEffectDist}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectDist}
%% \end{center}
%% \caption{Baseline/Concave effect distance \label{concave:BaselineConcaveEffectDist}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcaveEffectMag}{Baseline/Concave effect using cohesion/repulsion\label{concave:BaselineConcaveEffectMag}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectMag}
%% \end{center}
%% \caption{Baseline/Concave effect magnitude\label{concave:BaselineConcaveEffectMag}}
%% \end{figure}

Figure~\ref{concave:BaselineConcavePerimeter} shows the effect on the number of perimeter agents. Initially the perimeter size is minimally affected due to the swarms compression however after the expansion phase of the swarm (8 seconds) more perimeter agents are identified as concave edges are formed. As these concave edges are `straightened' they create further anomalies that ripple through the swarm. This rippling is identified by the erratic changes in the number of perimeter agents. After approximately 30 seconds the swarm has been forced into a less angular structure with curved edges and the number of perimeter agents falls below the minimum of the baseline. The shape of the swarm is still undergoing change following this and the perimeter count continues to fluctuate.
%PERIMETER8070CONCAVE.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcavePerimeter}{Baseline/Concave perimeter size\label{concave:BaselineConcavePerimeter}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcavePerimeter}
%% \end{center}
%% \caption{Baseline/Concave perimeter size\label{concave:BaselineConcavePerimeter}}
%% \end{figure}
The effect on the structure of the swarm caused by the concave perimeter agents moving towards the gap agents is to pull the internal agents forward. This pulling causes the swarm to develop a more rounded structure but the effect also have a negative impact. If the tolerance of the agent's movements (the difference between the agent ranges for repulsion and cohesion) is too small then the distortion effect of the concave reduction can create additional voids. The perimeter agents will then move so as to remove the defect~(Fig.~\ref{fig:OuterPerimeterJitter1}). Following the void creation the agents are now impacted by a second concave reduction from the newly created void and the anomaly on the perimeter edge `snaps' back closing the void~(Fig.~\ref{fig:OuterPerimeterJitter2}). This process repeats itself creating an instability in the number of perimeter agents which is highlighted in~Fig.~\ref{concave:BaselineConcavePerimeter} as the erratic change in the number of agents.

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcaveEffectPath1}{Baseline/Concave path effect (Full)\label{concave:BaselineConcaveEffectPath1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectPath1}
%% \end{center}
%% \caption{Baseline/Concave path effect\label{concave:BaselineConcaveEffectPath1}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcaveEffectPath2}{Baseline/Concave path effect (Zoomed)\label{concave:BaselineConcaveEffectPath2}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectPath2}
%% \end{center}
%% \caption{Baseline/Concave path effect\label{concave:BaselineConcaveEffectPath2}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcaveEffectDist8060}{Baseline/Concave effect distance (80/60)\label{concave:BaselineConcaveEffectDist8060}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectDist8060}
%% \end{center}
%% \caption{Baseline/Concave effect distance (80/60)\label{concave:BaselineConcaveEffectDist8060}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcaveEffectMag8060}{Baseline/Concave effect magnitude (80/60)\label{concave:BaselineConcaveEffectMag8060}}
% \begin{figure}
% \begin{center}
% \includegraphics[width=8cm]{figures/BaselineConcaveEffectMag8060}
% \end{center}
% \caption{Baseline/Concave effect magnitude (80/60)\label{concave:BaselineConcaveEffectMag8060}}
% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcavePerimeter8060}{Baseline/Concave perimeter size (80/60)\label{concave:BaselineConcavePerimeter8060}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcavePerimeter8060}
%% \end{center}
%% \caption{Baseline/Concave perimeter size (80/60)\label{concave:BaselineConcavePerimeter8060}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/Baseline8060End}{Baseline end\label{fig:BaselineEndPoint}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/Baseline8060End}
%% \end{center}
%% \caption{Baseline end\label{fig:BaselineEndPoint}}
%% \end{figure}
%COVERBASELINE8060COMPRESSEND.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/Concave8060End}{Concave reduction end\label{fig:ConcaveEndPoint}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/Concave8060End}
%% \end{center}
%% \caption{Concave reduction end\label{fig:ConcaveEndPoint}}
%% \end{figure}

@@

%COVERBASELINE8060.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcaveEffectPath80601}{Baseline/Concave path effect (80/60)\label{concave:BaselineConcaveEffectPath80601}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectPath80601}
%% \end{center}
%% \caption{Baseline/Concave path effect (80/60)\label{concave:BaselineConcaveEffectPath80601}}
%% \end{figure}

%COVERBASELINE8060.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/BaselineConcaveEffectPath80602}{Baseline/Concave path effect (80/60)\label{concave:BaselineConcaveEffectPath80602}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/BaselineConcaveEffectPath80602}
%% \end{center}
%% \caption{Baseline/Concave path effect (80/60)\label{concave:BaselineConcaveEffectPath80602}}
%% \end{figure}
With the tolerance levels set appropriately the impact of the concave reduction is to reduce the number of agents being identified as coordinators~(Fig.~\ref{concave:mobileSwarm1}). This reduction in perimeter size is due to a reduction in the number of anomalies in the swarm. The effect of the concave reduction on a convex (outer) perimeter is limited when a swarm is deployed in an almost circular manner as there is limited space for optimisation. The effect is more pronounced when a swarm is `malformed' with large anomalies producing concave edges.

@@

%COVERBASELINE4560-BASEEND.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/Baseline4560End}{Baseline end\label{fig:BaselineEndPoint4560}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Baseline4560End}
%% \end{center}
%% \caption{Baseline end\label{fig:BaselineEndPoint4560}}
%% \end{figure}

%COVERBASELINE4560END3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/Concave4560End}{Concave end\label{fig:ConcaveEndPoint4560}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Concave4560End}
%% \end{center}
%% \caption{Concave end\label{fig:ConcaveEndPoint4560}}
%% \end{figure}

@@

%COVERBASELINE4560.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/Concave4560-1}{Initial\label{fig:VoidConcaveReduction1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Concave4560-1}
%% \end{center}
%% \caption{Initial\label{fig:VoidConcaveReduction1}}
%% \end{figure}

%COVERBASELINE4560END2.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/Concave4560-2}{Partial\label{fig:VoidConcaveReduction2}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Concave4560-2}
%% \end{center}
%% \caption{Partial\label{fig:VoidConcaveReduction2}}
%% \end{figure}

%COVERBASELINE4560END3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/Concave4560-3}{Complete\label{fig:VoidConcaveReduction3}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/Concave4560-3}
%% \end{center}
%% \caption{Complete\label{fig:VoidConcaveReduction3}}
%% \end{figure}

@@

%SWARMHOLE-DIST-4560.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/ConcavePerimeter4560-DIST}{Concave reduction stability effect distance\label{voids:ConcavePerimeter4560-DIST}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/ConcavePerimeter4560-DIST}
%% \end{center}
%% \caption{Concave reduction stability effect distance\label{voids:ConcavePerimeter4560-DIST}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/ConcavePerimeter4560-DIST-2}{Concave reduction stability effect distance\label{voids:ConcavePerimeter4560-DIST-2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/ConcavePerimeter4560-MAG}{Concave reduction stability effect magnitude\label{voids:ConcavePerimeter4560-MAG}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/ConcavePerimeter4560-MAG-2}{Concave reduction stability effect magnitude\label{voids:ConcavePerimeter4560-MAG-2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/ConcavePerimeter4560-1}{Concave reduction perimeter effect\label{methods:ConcavePerimeter4560-1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/SwarmCoverage4560-1}{Agent movement comparison\label{voids:SwarmCoverage4560-1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/SwarmCoverage4560-2}{Agent movement comparison\label{voids:SwarmCoverage4560-2}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSlick}{Concave reduction oil slick surrounding\label{voids:OilSlick}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/OilSlick}
%% \end{center}
%% \caption{Concave reduction oil slick surrounding\label{voids:OilSlick}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillSimulator}
{Oil spill containment simulation\label{concave:OilSpillSimulation}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/OilSpillSimulator}
%% \end{center}
%% \caption{Oil spill containment simulation\label{concave:OilSpillSimulation}}
%% \end{figure}

@@

%COVERBASELINE8060OILSPILL1.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillBase1}{Initial\label{concave:OilSpillBase1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[with=5cm]{figures/OilSpillBase1}
%% \end{center}
%% \caption{Initial\label{concave:OilSpillBase1}}
%% \end{figure}
%COVERBASELINE8060OILSPILL3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillBase2}{Partial\label{concave:OilSpillBase2}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillBase2}
%% \end{center}
%% \caption{Partial\label{concave:OilSpillBase2}}
%% \end{figure}
%COVERBASELINE8060OILSPILL3.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillBase3}{End\label{concave:OilSpillBase3}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillBase3}
%% \end{center}
%% \caption{End\label{concave:OilSpillBase3}}
%% \end{figure}

@@

%COVERBASELINE8060OILSPILLCONCAVE1.py 
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillConcave1}{Initial\label{concave:OilSpillConcave1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillConcave1}
%% \end{center}
%% \caption{Initial\label{concave:OilSpillConcave1}}
%% \end{figure}

%COVERBASELINE8060OILSPILLCONCAVE2.py 
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillConcave2}{Partial\label{concave:OilSpillConcave2}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/OilSpillConcave2}
%% \end{center}
%% \caption{Partial\label{concave:OilSpillConcave2}}
%% \end{figure}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillConcave3}{End\label{concave:OilSpillConcave3}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillPerimeter8060-DIST-1}{Oil spill containment distance\label{concave:OilSpillPerimeter8060-DIST-1}}

@@

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillPerimeter8060-MAG-1}{Oil spill containment magnitude\label{concave:OilSpillPerimeter8060-MAG-1}}

@@

%PERIMETEROILSPILL.py
\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=8.3cm]{figures/OilSpillPerimeter8060-1}{Swarm perimeter size comparison\label{concave:OilSpillPerimeter8060-1}}
%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=8cm]{figures/OilSpillPerimeter8060-1}
%% \end{center}
%% \caption{Swarm perimeter size comparison\label{concave:OilSpillPerimeter8060-1}}
%% \end{figure}
